Strong lensing selection effects

### 2022-08-15 paper/seleff.tex
Using i-band instead of g-band. Started bias plots

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{lens_observable_bias.eps}
\caption{
Bias on lens observable properties as a function of the minimum Einstein radius.
First panel: median redshift.
Second panel: median observed stellar mass.
Third panel: median half-light radius at an observed mass of $\log{\mobs}=11.4$.
Fourth panel: median axis ratio.
In each panel, the black dashed line indicates the value of the parent population.
Error bars indicate the standard deviation of the mean of the lens sample.
}
\end{figure}
